---
title: "Rsynaptome Output:"
author: "Rsynaptome Toolkit"
output:
  html_document:
    fig_caption: yes
    fig_height: 8
    fig_width: 8
    echo: FALSE
    highlight: pygments
    number_sections: yes
    theme: cerulean
    toc: yes
    toc_depth: 3
---


```{r setup, echo = FALSE}
opts_chunk$set(cache=FALSE, echo=FALSE, fig.height = 6, fig.width= 6,
               warning=FALSE, message=FALSE, fig.show='hold',
               comment="#", fig.keep='low')
```

# Heatmap of scaled data
```{r cc-heatmap}
if(use.plotly){
  tryCatch(ggplotly(p.heat(dat, TRUE)))
} else {
  tryCatch(p.heat(dat, FALSE))
}
```

# Violin Plot
```{r cc-violin, fig.height = gg.violin.h, fig.width = gg.violin.w}
if(use.plotly){
  tryCatch(ggplotly(p.violin(dat)))
} else {
  tryCatch(print(p.violin(dat)))
}
```

# Correlation Plot
```{r cc-corr}
tryCatch(p.cor(dat))
```

# Outlier Plots
```{r cc-outlier}
if(use.plotly){
  tryCatch(ggplotly(p.outlier(dat)))
} else {
  tryCatch(print(p.outlier(dat)))
}

```{r cc-which}
if(!is.null(dim(dat[outliers, ]))){
  if(use.plotly){
    tryCatch(ggplotly(p.heat(dat[outliers, ], FALSE)))
  } else {
    tryCatch(print(p.heat(dat[outliers, ], FALSE)))
  }
}
```

# Cumulative Variance 
```{r cc-cumsum}
if(use.plotly){
  tryCatch(ggplotly(p.cumvar(dat)))
} else {
  tryCatch(print(p.cumvar(dat)))
}
```

# Pairs Plots 
```{r cc-pairs, fig.height = 8, fig.width = 8}
tryCatch(p.pairs(dat))
```

# BIC Plot
```{r cc-bic}
tryCatch(p.bic(dat))
```

